---
title: "Exam 1 Prep"
author: "Elizabeth Bekele"
date: "DATA 2401"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Homework 2
1. Create a variable `hometown` that stores the city you consider your hometown as a string. 

```{r}
hometown <- 'Houston'
hometown
```

2. Assign your name to the variable `my_name`
```{r}
my_name <- 'Liz'
my_name
```

3. Assign your height (in inches) to a variable `my_height`
```{r}
my_height <- 66
my_height
```

4. Create a variable `puppies` equal to the number of puppies you'd like to have
```{r}
puppies <- 3
puppies
```

5. Create a variable `puppy_price`, which is how much you think a puppy costs
```{r}
puppy_price <- 1500
puppy_price
```

6. Create a variable `total_cost` that has the total cost of all of your puppies (use the variables you created in the previous questions)
```{r}
total_cost <- puppies * puppy_price
total_cost
```

7. Create a boolean variable `too_expensive`, that is set to TRUE if the cost is greater than $1,000 (use your variables created in the previous questions)
```{r}
too_expensive <- total_cost > 1000
too_expensive
```

8. Create a variable `max_puppies`, which is the number of puppies you can afford for $1,000
```{r}
max_puppies <- 1000/total_cost
max_puppies
```

9.  We can't have partial puppies. Round `max_puppies` down to a whole number (you might use a function called `floor`, type `?floor` in your R console for more information), save that as a new variable `actual_max_puppies`
```{r}
actual_max_puppies <- floor(max_puppies)
actual_max_puppies
```