---
title: "Exam 1 Prep"
author: "Elizabeth Bekele"
date: "DATA 2401"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework 1 
## Mainly plotting, stuff 
### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 variables: dataset (indicates which dataset the data are from), x (x-values), y (y-values). 

### Exercise 2
Below is a plot of the dino set. The correlation coefficient, r, is -0.064. However, we would not normally calculate this since the plot is not linear.

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plot the x and y cordinates of the star data set:


```{r plot-star, fig.height=5, fig.width=7}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the correlation between x and y in the star data set:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The r of star (-0.063) is greater than the r of dino (-0.064).


### Exercise 4

Plot the x and y coordinates of the circle data set:

```{r plot - circle, fig.height=5, fig.width=7}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the correlation coefficient of circle data:

```{r cor - circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The r of circle (-0.068) is less than the r of dino (-0.064).

### Exercise 5

Plot all data sets at once and calculate their summary correlation coefficients. 

```{r plot - all, fig.height=10, fig.width=10}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols 
  theme(legend.position = "none")
```

Now, calculate the summary correlation coefficients

``` {r - coef- all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

# Homework 2
1. Create a variable `hometown` that stores the city you consider your hometown as a string. 

```{r}
hometown <- 'Houston'
hometown
```

2. Assign your name to the variable `my_name`
```{r}
my_name <- 'Liz'
my_name
```

3. Assign your height (in inches) to a variable `my_height`
```{r}
my_height <- 66
my_height
```

4. Create a variable `puppies` equal to the number of puppies you'd like to have
```{r}
puppies <- 3
puppies
```

5. Create a variable `puppy_price`, which is how much you think a puppy costs
```{r}
puppy_price <- 1500
puppy_price
```

6. Create a variable `total_cost` that has the total cost of all of your puppies (use the variables you created in the previous questions)
```{r}
total_cost <- puppies * puppy_price
total_cost
```

7. Create a boolean variable `too_expensive`, that is set to TRUE if the cost is greater than $1,000 (use your variables created in the previous questions)
```{r}
too_expensive <- total_cost > 1000
too_expensive
```

8. Create a variable `max_puppies`, which is the number of puppies you can afford for $1,000
```{r}
max_puppies <- 1000/total_cost
max_puppies
```

9.  We can't have partial puppies. Round `max_puppies` down to a whole number (you might use a function called `floor`, type `?floor` in your R console for more information), save that as a new variable `actual_max_puppies`
```{r}
actual_max_puppies <- floor(max_puppies)
actual_max_puppies
```


# Homework 3
1. Create a vector `even` that holds the even numbers from 1 to 100
2.  Using the `all()` function and `%%` (modulo) operator, confirm that all of the numbers in your `even` vector are even
```{r}
#Problem 1
even <- seq(from = 2, to = 102, by = 2)

#Problem 2
all(even %% 2 == 0)
```


3. Create a vector `phone_numbers` that contains the numbers 2, 8, 1, 3, 3, 0, 8, 0, 0, 4
4.  Create a vector `prefix` that has the first three elements of `phone_numbers`
5. Create a vector `small` that has the values of `phone_numbers` that are less than or equal to 5
6. Create a vector `large` that has the values of `phone_numbers` that are strictly greater than 5
7. Replace the values in `phone_numbers` that are larger than 5 with the number 5
8.  Replace every odd-numbered value in `phone_numbers` with the number 0

> For question 4, please don't just do 2,8,1, use indexing! For questions 5 through 8, you should use not use "hard coding" for the indexes. 

```{r}
#Problem 3
phone_numbers <- c(2, 8, 1, 3, 3, 0, 8, 0, 0, 4)

#Problem 4
prefix <- phone_numbers[1:3]
prefix

#Problem 5
small <- phone_numbers[phone_numbers <= 5]
small

#Problem 6
large <- phone_numbers[phone_numbers > 5]
large

#Problem 7
phone_numbers[phone_numbers > 5] <- 5
phone_numbers

#Problem 8
phone_numbers[phone_numbers %% 2 != 0] <- 0
phone_numbers
```

9. Create a vector of 100 simulated dice rolls called `fifty_rolls_1`
10. Create a second vector of 100 simulated dice rolls called `fifty_rolls_2`
11. If you pretend these two die are rolled at the same time, find how many of the 100 two-dice rolls are doubles. (doubles are when the two die have the same number)

```{r}
# this function makes it so that your "random" number generator is at the same spot as mine. 
set.seed(102389) ## leave this here to keep the randomness consistent

#Problem 9
fifty_rolls_1 <- sample(1:6, 100, replace = T)
fifty_rolls_1

#Problem 10
fifty_rolls_2 <- sample(1:6, 100, replace = T)
fifty_rolls_2

#Problem 11
length(fifty_rolls_1[fifty_rolls_1 == fifty_rolls_2])
```

Extra Credit, 5 points:

12. Make a function that does 9, 10, and 11 together for you, and returns the number of doubles. (Note: functions don't have to have input arguments!)

```{r}
set.seed(102389)

combo <- function(){
  fifty_rolls_1 <- sample(1:6, 100, replace = T)
  fifty_rolls_2 <- sample(1:6, 100, replace = T)
  return (length(fifty_rolls_1[fifty_rolls_1 == fifty_rolls_2]))
}

combo()
```

