---
title: "Exam 1 Prep"
author: "Elizabeth Bekele"
date: "DATA 2401"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Homework 2
1. Create a variable `hometown` that stores the city you consider your hometown as a string. 

```{r}
hometown <- 'Houston'
hometown
```

2. Assign your name to the variable `my_name`
```{r}
my_name <- 'Liz'
my_name
```

3. Assign your height (in inches) to a variable `my_height`
```{r}
my_height <- 66
my_height
```

4. Create a variable `puppies` equal to the number of puppies you'd like to have
```{r}
puppies <- 3
puppies
```

5. Create a variable `puppy_price`, which is how much you think a puppy costs
```{r}
puppy_price <- 1500
puppy_price
```

6. Create a variable `total_cost` that has the total cost of all of your puppies (use the variables you created in the previous questions)
```{r}
total_cost <- puppies * puppy_price
total_cost
```

7. Create a boolean variable `too_expensive`, that is set to TRUE if the cost is greater than $1,000 (use your variables created in the previous questions)
```{r}
too_expensive <- total_cost > 1000
too_expensive
```

8. Create a variable `max_puppies`, which is the number of puppies you can afford for $1,000
```{r}
max_puppies <- 1000/total_cost
max_puppies
```

9.  We can't have partial puppies. Round `max_puppies` down to a whole number (you might use a function called `floor`, type `?floor` in your R console for more information), save that as a new variable `actual_max_puppies`
```{r}
actual_max_puppies <- floor(max_puppies)
actual_max_puppies
```


# Homework 3
1. Create a vector `even` that holds the even numbers from 1 to 100
2.  Using the `all()` function and `%%` (modulo) operator, confirm that all of the numbers in your `even` vector are even
```{r}
#Problem 1
even <- seq(from = 2, to = 102, by = 2)

#Problem 2
all(even %% 2 == 0)
```


3. Create a vector `phone_numbers` that contains the numbers 2, 8, 1, 3, 3, 0, 8, 0, 0, 4
4.  Create a vector `prefix` that has the first three elements of `phone_numbers`
5. Create a vector `small` that has the values of `phone_numbers` that are less than or equal to 5
6. Create a vector `large` that has the values of `phone_numbers` that are strictly greater than 5
7. Replace the values in `phone_numbers` that are larger than 5 with the number 5
8.  Replace every odd-numbered value in `phone_numbers` with the number 0

> For question 4, please don't just do 2,8,1, use indexing! For questions 5 through 8, you should use not use "hard coding" for the indexes. 

```{r}
#Problem 3
phone_numbers <- c(2, 8, 1, 3, 3, 0, 8, 0, 0, 4)

#Problem 4
prefix <- phone_numbers[1:3]
prefix

#Problem 5
small <- phone_numbers[phone_numbers <= 5]
small

#Problem 6
large <- phone_numbers[phone_numbers > 5]
large

#Problem 7
phone_numbers[phone_numbers > 5] <- 5
phone_numbers

#Problem 8
phone_numbers[phone_numbers %% 2 != 0] <- 0
phone_numbers
```

9. Create a vector of 100 simulated dice rolls called `fifty_rolls_1`
10. Create a second vector of 100 simulated dice rolls called `fifty_rolls_2`
11. If you pretend these two die are rolled at the same time, find how many of the 100 two-dice rolls are doubles. (doubles are when the two die have the same number)

```{r}
# this function makes it so that your "random" number generator is at the same spot as mine. 
set.seed(102389) ## leave this here to keep the randomness consistent

#Problem 9
fifty_rolls_1 <- sample(1:6, 100, replace = T)
fifty_rolls_1

#Problem 10
fifty_rolls_2 <- sample(1:6, 100, replace = T)
fifty_rolls_2

#Problem 11
length(fifty_rolls_1[fifty_rolls_1 == fifty_rolls_2])
```

Extra Credit, 5 points:

12. Make a function that does 9, 10, and 11 together for you, and returns the number of doubles. (Note: functions don't have to have input arguments!)

```{r}
set.seed(102389)

combo <- function(){
  fifty_rolls_1 <- sample(1:6, 100, replace = T)
  fifty_rolls_2 <- sample(1:6, 100, replace = T)
  return (length(fifty_rolls_1[fifty_rolls_1 == fifty_rolls_2]))
}

combo()
```

